Computing Entropies with Nested Sampling

### 2017-12-10 talk/ms-abridged.tex
Two slides into one
Fewer slides

\begin{center}
\includegraphics[width=0.6\textwidth]{entropy1.pdf}
\end{center}

\begin{center}
\includegraphics[width=0.6\textwidth]{entropy2.pdf}
\end{center}

@@

% New slide
\begin{frame}
\frametitle{Some entropies in Bayesian statistics}
Written in terms of parameters $\theta$ and data
$d$, for Bayesian purposes.

@@

% New slide
\begin{frame}
\frametitle{Some entropies in Bayesian statistics}

@@

% New slide
\begin{frame}
\frametitle{Pre-data considerations}

We might want to know {\em how relevant the data is to the parameters},
before learning the data. We might want to optimise that quantity for
experimental design. But it's nasty, especially if there are nuisance
parameters.
\end{frame}

@@

% New slide
\begin{frame}
\frametitle{Poisson process view of NS}

The number of NS iterations taken
to enter a small region (defined by a likelihood threshold) 
is an unbiased estimator of the log-probability
of that region!\vspace{0.7em}

Also, $\pi(\theta)$ can be any distribution (needn't be
a prior) and $L(\theta)$ any scalar function. Opportunities here...

>>>>

@@

% New slide
\begin{frame}
\frametitle{Some entropies in Bayesian statistics}
Written in terms of parameters $\theta$ and data
$d$, for Bayesian purposes. These are relevant to
experimental design...

@@

\pause
\pause
\pause
\pause
\pause

@@

@@

%% New slide
%\begin{frame}
%\frametitle{Poisson process view of NS}

%The number of NS iterations taken
%to enter a small region (defined by a likelihood threshold) 
%is an unbiased estimator of the log-probability
%of that region!\vspace{0.7em}

%Also, $\pi(\theta)$ can be any distribution (needn't be
%a prior) and $L(\theta)$ any scalar function. Opportunities here...
